### 2015-08-03 chapters/ipa_meets_unicode.tex
edits

Although the original IPA alphabet was a list of symbols with pronunciation examples 
from words in different languages, in 1900 the symbols were organized into chart and 
given phonetic feature labels for consonants (e.g.\ for manner of articulation: `plosives', 
`nasales', `fricatives'; for place of articulation: `bronchials', `laryngeales', `labiales') 
and for vowels (`fermeées', `mi-fermeées', `mi-overtes', `overtes'). Over the last century 
or so, the structure of the chart has changed with increases in phonetic knowledge, and 
thus like notational systems in other scientific disciplines, the IPA reflects facts and 
theories (of phonetic knowledge) that have developed over time. It is natural then that 
the IPA is modified occasionally to accommodate scientific innovations and discoveries. 
(In fact, this is part of the Association's mandate.) These changes are captured in 
the revisions to the IPA.\footnote{For a detailed history see: 
\url{https://en.wikipedia.org/wiki/History\_of\_the\_International\_Phonetic_Alphabet}}

Over the years there has been several revisions, many minor. For example, 
articulation labels -- what we now call features even though the IPA avoids this term -- 
have changed (e.g.\ `lips', `throat', `rolled'). Phonetic symbol values have changed 
(e.g.\ voiceless is no longer marked by <h>). Symbols have been dropped (e.g.\ the 
caret diacritic denoting `long and narrow' is longer used). And many symbols have 
been added to reflect contrastive sounds found in the world's very diverse 
phonological systems.

>>>>

Although the original IPA alphabet was a list of symbols with pronunciation examples 
from words in different languages, in 1900 the symbols were organized into chart form and 
given phonetic feature labels for consonants (e.g.\ for manner of articulation: `plosives', 
`nasales', `fricatives'; for place of articulation: `bronchials', `laryngeales', `labiales') 
and for vowels (`fermeées', `mi-fermeées', `mi-overtes', `overtes'). Over the last century 
or so, the structure of the chart has changed with increases in phonetic knowledge, and 
thus like notational systems in other scientific disciplines, the IPA reflects facts and 
theories (of phonetic knowledge) that have developed over time. It is natural then that 
the IPA is modified occasionally to accommodate scientific innovations and discoveries. 
(In fact, this is part of the Association's mandate.) These changes are captured in 
the revisions to the IPA.\footnote{For a detailed history see: 
\url{https://en.wikipedia.org/wiki/History\_of\_the\_International\_Phonetic_Alphabet}}

Over the years there has been many revisions, most minor. For example, 
articulation labels -- what we now call features even though the IPA avoids this term -- 
have changed (e.g.\ `lips', `throat', `rolled'). Phonetic symbol values have changed 
(e.g.\ voiceless is no longer marked by <h>). Symbols have been dropped (e.g.\ the 
caret diacritic denoting `long and narrow' is longer used). And many symbols have 
been added to reflect contrastive sounds found in the world's very diverse 
phonological systems.
